---
title: "BAX-401-HW2"
author: "Sayar Banerjee"
date: "2022-10-26"
output: html_document
---

# Read Data
```{r}
df <-read_excel("HW2_MultimediaHW.xlsx")
```


# Descriptive Statistics

## Sales with ADV_Total, ADV_Offline, ADV_Online
```{r}
scatter.smooth(df$`Sales (units)`, df$ADV_Total)
scatter.smooth(df$`Sales (units)`, df$ADV_Offline)
scatter.smooth(df$`Sales (units)`, df$ADV_Online)
```

```{r}
corrplot::corrplot(cor(df), method = 'number')
```

## Transform Variables (Square Root) and Sales lag
```{r}
for (i in 3:ncol(df)) {
  df[,i] <- sqrt(df[, i])
}
lagSales <-Lag(df$`Sales (units)`,shift=1)
df$lagSales <-lagSales
```

## Plot again
```{r}
corrplot::corrplot(cor(df), method = 'number')
```
## Build model

### LagSales, ADV_OFfline, ADV_online, lagSales * ADV_Offline
```{r}
lagSales <-Lag(df$`Sales (units)`,shift=1)

synergy_without_intercept <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline + df$ADV_online + lagSales * df$ADV_Offline - 1)
summary(synergy_without_intercept)
AIC(synergy_without_intercept)
BIC(synergy_without_intercept)
```

### LagSales, Offline, Search, Portal, Search * Portals
```{r}

synergy_without_intercept <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline + df$Search + df$Portals + df$Search * df$Portals  - 1)
summary(synergy_without_intercept)
AIC(synergy_without_intercept)
BIC(synergy_without_intercept)
```

### LagSales, Offline, Search, Portal, LagSales * Offline * Search, LagSales * Offline * Portal
```{r}
lagSales <-Lag(df$`Sales (units)`,shift=1)

synergy_without_intercept <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline + df$Search + df$Portals + df$Search * df$Portals + df$ADV_Offline * lagSales +  df$ADV_Offline * lagSales * df$Portals + df$ADV_Offline * lagSales *  df$Search + df$ADV_Offline * df$Search + df$ADV_Offline * df$Portals + lagSales * df$Search + lagSales * df$Portals + lagSales * df$ADV_Offline * df$Search * df$Portals - 1)
summary(synergy_without_intercept)
AIC(synergy_without_intercept)
BIC(synergy_without_intercept)
```

### LagSales, ADV_Offline, Portal, LagSales * Portals
```{r}
synergy_without_intercept <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline + df$Portals + df$ADV_Offline * lagSales  - 1)
summary(synergy_without_intercept)
AIC(synergy_without_intercept)
BIC(synergy_without_intercept)
```

### LagSales, ADV_Offline, Search, ADV_Offline * Search
```{r}
synergy_without_intercept <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline + df$Search + df$ADV_Offline * lagSales  - 1)
summary(synergy_without_intercept)
AIC(synergy_without_intercept)
BIC(synergy_without_intercept)
```

### Looking at interaction
```{r}
mod1 <-lm(df$`Sales (units)` ~ df$ADV_online + df$ADV_Offline - 1)
summary(mod1)
AIC(mod1)
BIC(mod1)

mod2 <-lm(df$`Sales (units)` ~ df$ADV_online + df$ADV_Offline + df$ADV_online * df$ADV_Offline - 1)
summary(mod2)
AIC(mod2)
BIC(mod2)

mod3 <-lm(df$`Sales (units)` ~ lagSales + df$ADV_online + df$ADV_Offline - 1)
summary(mod3)
AIC(mod3)
BIC(mod3)

mod4 <-lm(df$`Sales (units)` ~ lagSales + df$ADV_online + df$ADV_Offline + df$ADV_online * df$ADV_Offline - 1)
summary(mod4)
AIC(mod4)
BIC(mod4)

#mod5 <-lm(df$`Sales (units)` ~ lagSales + df$ADV_Offline  - 1)
#summary(mod5)
#AIC(mod5)
#BIC(mod5)

mod5 <-lm(df$`Sales (units)` ~ lagSales + df$Search * df$Portals + df$Search + df$Portals - 1)
summary(mod5)
```

## Use stepwise regression
```{r}
# Remove aggregate and empty columns
df <- subset(df, select = -c(Months, ADV_Total, ADV_Offline, ADV_online, SocialMedia))
step_model_both <-step(lm(df$`Sales (units)` ~ . -1, data=df), direction="backward")
summary(step_model_both)
```

## Use new regression
```{r}
#Search/Portals can be removed based on the fact that they have a strong correlation with each other in the correlation plots.
# Keep one. Remove the other one.
final_tuned_model <-lm(df$`Sales (units)` ~ df$Catalogs_Winback + df$Catalogs_NewCust + df$Search + df$Retargeting + df$lagSales - 1)
summary(final_tuned_model)
```